\begin{frame}{Disability Support Services}
    If you have a physical, psychological, medical or learning disability that may impact your course work, please contact Disability Support Services, ECC (Educational Communications Center) Building, Room 128, (631) 632-6748. They will determine with you what accommodations, if any, are necessary and appropriate. All information and documentation is confidential.

    Students who require assistance during emergency evacuation are encouraged to discuss their needs with their professors and Disability Support Services.
    For procedures and information go to the following website:
    \url{http://www.stonybrook.edu/ehs/fire/disabilities}
\end{frame}

\begin{frame}{Academic Integrity}
    Each student must pursue his or her academic goals honestly and be personally accountable for all submitted work. Representing another person's work as your own is always wrong.  Faculty are required to report any suspected instances of academic dishonesty to the Academic Judiciary.  Faculty in the Health Sciences Center (School of Health Technology \& Management, Nursing, Social Welfare, Dental Medicine) and School of Medicine are required to follow their school-specific procedures. For more comprehensive information on academic integrity, including categories of academic dishonesty, please refer to the academic judiciary website at
    \url{http://www.stonybrook.edu/uaa/academicjudiciary/}
\end{frame}

\begin{frame}{Critical Incident Management}
    Stony Brook University expects students to respect the rights, privileges, and property of other people. Faculty are required to report to the Office of Judicial Affairs any disruptive behavior that interrupts their ability to teach, compromises the safety of the learning environment, or inhibits students' ability to learn.  Faculty in the HSC Schools and the School of Medicine are required to follow their school-specific procedures.
\end{frame}
